Geometric Control for Autonomous Landing on Asteroid Itokawa using visual localization

### 2017-08-29 manuscript.tex
Add initial submission to arxiv
Fix some typos

\begin{abstract}
    This paper considers the coupled orbit and attitude dynamics of a dumbbell spacecraft around an asteroid. 
    Geometric methods are used to derive the coupled equations of motion, defined on the configuration space of the special Euclidean group, and then a nonlinear controller is designed to enable trajectory tracking of desired landing trajectories.
    Rather than relying on sliding mode control or optimization based methods, the proposed approach avoids the increased control utilization and computational complexity inherent in other techniques.
    The nonlinear controller is used to track a desired landing trajectory to the asteroid surface. 
    A monocular imaging sensor is used to provide position and attitude estimates using visual odometry to enable relative state estimates.
    We demonstrate this control scheme with a landing simulation about asteroid Itokawa.
\end{abstract}

@@

Determination of the state of the spacecraft is typically dependent on ground based observations with sporadic state updates.
An additional capability is possible by using on-board sensors to estimate the state of the spacecraft relative to the asteroid~\cite{kubota2003,miso1999}.
We seek to incoporate localization using monocular images into the geometric nonlinear controller. 
This will offer the ability to increase the accuracy and frequency of state estimates and allow for closed loop control for landing operations. 
The use of imagery also enables the use of computer vision algorithms and tools to estimate the shape and motion of the asteroid.
The combination of visual localization and geometric control is a new avenue for the operation of spacecraft near asteroids.

@@

\subsection{Itokawa Shape Model and Simulated Imagery}\label{sec:imagery}
In this work, we consider trajectories about asteroid 25413 Itokawa.
Itokawa was the target of the Hayabusa mission and detailed shape and surface maps have been generated~\cite{kawaguchi2006,tanimoto2013,fujiwara2006}.
We use the estimated rotation period of \SI{12.1}{\hour} with a nominal density of \SI{1.9}{\gram\per\centi\meter\cubed} in the polyhderon potential model.
The shape model is composed of \num{786432} triangular faces and a rendering of the asteroid is provided in~\cref{fig:itokawa_3d}.
A highly detailed model is used for the shape of the asteroid to provide a more detailed and feature rich imaging target. 
However, the polyhedron potential model uses a much coarser shape composed of \num{64} faces. 
This greatly reduces the complexity of the potential model without a significant difference in the qualitative nature of the dynamic environment.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.5\textwidth, keepaspectratio]{figures/itokawa_blender.png}
    \caption{Blender Rendering of Asteroid 25413 Itokawa}
    \label{fig:itokawa_3d}
\end{figure}

Images of asteroid Itokawa are simulated using Blender, a free and open-source computer graphics software program~\cite{blenderfoundation1995--2017}.
Blender is primarily used by the animation and computer modeling fields to create computer generated images, videos and animations for films and video games. 
Blender offers the capability of accurately modelling the various effects of camera, lighting, and surface properties of a scene using the \texttt{cycles} path-tracing rendering engine.
A unique feature is the ability to compile the Blender rendering software as a Python module.
This allows one to use the capabilities of Blender through a Python API in personal scripts and functions programmatically, rather than through a desktop based graphical interface.
A camera is simulated within Blender with the parameters shown in~\cref{tab:camera_parameters}, which are chosen to emulate the primary sensor of the NEAR spacecraft~\cite{hawkins1997}.
\begin{table}
    \centering
\begin{tabular}{llr}  
\toprule
Parameter & Description &  Value\\
\midrule
FOV & horizontal field of view & \SI{2.25}{\degree}       \\
    &    vertical field of view  & \SI{2.90}{\degree}\\
Image Size & horizontal & \SI{537}{\px}\\
           & vertical & \SI{244}{\px}\\
\(f\)& focal length & \SI{167.35}{\milli\meter}\\
\bottomrule
\end{tabular}
\caption{Camera parameters used in simulation~\label{tab:camera_parameters}}
\end{table}

@@

In order to determine the attitude control input, we first define a desired attitude tracking command.
An arbitrary smooth attitude tracking command \( R_d (t) \in \SO \) is given as a function of time.
The corresponding angular velocity command is obtained using the attitude kinematics equation, \( \hat{\Omega}_d = R_d^T \dot{R}_d \).
With the desired attitude command, we then define the errors associated with the attitude and angular velocity.
The attitude and angular velocity tracking errors must be careful chosen to remain on the tangent bundle of \SO.
First, an attitude error function is defined on \( \SO \times \SO \) as
\begin{align}\label{eq:attitude_error_function}
    \Psi(R, R_d) = \frac{1}{2} \tr{I - R_d^T R}.
\end{align}
This positive definite function parameterizes the error between the current attitude, \( R \), and the desired attitude command \( R_d \).
Using the variations of \( \Psi \) gives the attitude tracking error vector \( e_R \in \R^3 \) as
\begin{align}\label{eq:attitude_error_vector}
    e_R = \frac{1}{2} \parenth{R_d^T R - R^T R_d^\vee}.
\end{align}
After further manipulation and using the attitude kinematics equation from~\cref{eq:attitude_kinematics}, it is possible to define the angular veloicty tracking error \( e_\Omega \in \R^3 \) as
\begin{align}\label{eq:angular_velocity_error_vector}
    e_\Omega = \Omega - R^T R_d \Omega_d .
\end{align}
With the properly defined attitude error vectors the rotational control input is defined as 
\begin{align*}\label{eq:rotational_control}
    \vb{u}_m = - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - J \parenth{\hat{\Omega} R^T R_d \Omega_d - R^T R_d \dot{\Omega}_d} - \vb{M}_1 - \vb{M_2} 
\end{align*}
where \( k_R, k_\Omega \) are positive controller constants.

@@

We seek to utilize well-proven methods in the computer vision and robotics community to first localize the position of the spacecraft from visual imagery.
A secondary step, which is left to a subsequent publication, is then to use this imagery to autonomously update the position of the spacecraft while simultaneously mapping the surface. 
We utilize the state of the art ORB-SLAM implementation to estimate the state of the spacecraft using monocular images~\cite{mur-artal2015}.
This method provides a feature based monocular SLAM system that can operate in real-time for a wide variety of environments. 
ORB-SLAM builds on proven methods in the robotics community to create a custom SLAM system that provides for autonomous tracking and mapping in an unknown environment. 
The first step in ORB-SLAM is to determine accurate features within an image that are most easily recognized in subsequent images. 
This ``feature-extraction'' stage uses the FAST feature detector to determine suitable features, and then the ORB feature descriptor to a store a compact, scale-invariant description of the feature properties.
Next, these features are matched to subsequent images in a ``feature-matching'' stage to determine correspondance between subsequent images. 
For example,~\cref{fig:itokawa_feature_matching} shows a demonstration of features computed in two view of asteroid Itokawa. 
In addition, the correspondance is accurately computed between matching features as shown by the horizontal lines across both images.
From these correspondances, the pose of the camera system is estimated and predicted forward in time using a constant velocity model.
In a simultaenous thread, the ORB-SLAM system builds a local map and stores feature data in order to perform loop closure in the event of returning to a previously imaged location.
We utilize ORB-SLAM to provide an estimate of the position of the rigid spacecraft and will use this estimate to compute the control input.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth,keepaspectratio]{figures/itokawa_feature_matching.png}
    \caption{Demonstration of feature detection and matching between simulated images of asteroid 25413 Itokawa}
    \label{fig:itokawa_feature_matching}
\end{figure}
\section{Numerical Simulation}\label{sec:simulation}

We present a numerical simulation of a rigid dumbbell about asteroid Itokawa.
The dumbbell spacecraft is composed of two equal masses, \( m_1, m_2 = \SI{500}{\kilo\gram} \), seperated by \( l = \SI{3}{\meter} \).
The dumbbell body frame is defined with the first body fixed axis, \( \vb{b}_1 \), originating at the center of mass of the spacecraft and directed along the vector from \( m_1 \) towards \( m_2 \).
The other two axes of the spacecraft fixed frame are chosen orthogonal to the \( \vb{b}_1 \) and lie in the plane orthogonal to the dumbbell axis of symmetry. 
A camera, using the parameters from~\cref{tab:camera_parameters}, is aligned with the \( \vb{b}_1 \) axis and used to feed image data to the ORB-SLAM system.
A numerical simulation is used to demonstrate the geometric control of the coupled motion of the spacecraft, and the ability to estimate the motion of the spacecraft from monocular imagery.

@@

The desired attitude command is chosen such that the spacecraft camera axis, \( \vb{b}_1 \), is directed along the nadir towards the asteroid.
It is sufficient to define two orthogonal vectors to uniquely determine the attitude of the spacecraft.
The \( \vb{b}_{3d} \) vector is chosen to lie in the plane spanned by \(\vb{b}_{1d} \) and \( \vb{e}_3 = \vb{f}_3 \).
The desired attitude command is defined as
\begin{align}
    \vb{b}_{1d} &= - \frac{\vb{x}}{\norm{\vb{x}}} , \\
    \vb{b}_{3d} &= \frac{\vb{f}_3 - \parenth{\vb{f}_3 \cdot \vb{b}_{1d}} \vb{b}_{1d}}{\norm{\vb{f}_3 - \parenth{\vb{f}_3 \cdot \vb{b}_{1d}} \vb{b}_{1d}}}, \\
    \vb{b}_{2d} &= \vb{b}_{3d} \times \vb{b}_{1d} , \\
R_d &= \begin{bmatrix} \vb{b}_{1d} & \vb{b}_{2d} & \vb{b}_{3d} \end{bmatrix} .
\end{align}
The camera axis is aligned with the spacecraft \( \vb{b}_ 1 \) axis, which is direted towards the asteroid, throughout the landing trajectory as the spacecraft moves in the equatorial plane of the asteroid.

The simulation is carried out over \SI{7200}{\second} with the spacecraft following a circular trajectory for the first \SI{3600}{\sec} before vertically descending in the body fixed frame for the last \SI{3600}{\second}.
\Cref{fig:true_landing_trajectory} shows a view from the positive \( \vb{f}_3 \) pole of the asteroid of the simulated trajectory. 
The position of the center of mass of the dumbbell is shown in blue, while the pointing direction of the camera axis is defined in red. 
The attitude of the dumbbell is displayed at several points along the trajectory demonstraiting the pointing of the camera. 
Furthermore, asteroid Itokawa is shown in its final orientation at the completion of the landing simulation. 
\Cref{fig:pos_components} shows that the nonlinear controller is able to accurately track the desired translational trajectory for the duration of the simulation.
\begin{figure}[htbp]
    \captionsetup[subfigure]{position=b}
    \centering
    \subcaptionbox{Planar view of landing trajectory\label{fig:true_landing_trajectory}}{\includegraphics[width=0.5\textwidth]{figures/traj_fig.pdf}}~
    \subcaptionbox{Position of spacecraft in the inertial frame\label{fig:pos_components}}{\includegraphics[width=0.5\textwidth]{figures/pos_fig.pdf}}
    \caption{Landing trajectory to asteroid Itokawa~\label{fig:position}}
\end{figure}

Concurrent with the simulation, we generate images of Itokawa using Blender, as described earlier.
The images are generated at a rate of \SI{1}{\hertz} and stored for post processing and one exampel view is shown in~\cref{fig:example_image}. 
From these images we estimate the position of the camera relative to the asteroid using monocular localization.
In this work, we demonstrate the ability to generate realistic imagery and the processing of these images to determine a state estimate of the camera pose.
In future work, we seek to use this state estimate in a closed-loop controller to enable a fully-autonomous control system for the spacecraft. 
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/test000837.png}
    \caption{Example image of Itokawa at \( t = \SI{837}{\second}\)\label{fig:example_image}}
\end{figure}
From each image, a series of features are detected and tracked between subsequent frames.
A visualization of this process is shown in~\cref{fig:orbslam_mappoints} which shows the tracked features of the image in green.
From these tracked features it is possible to estimate the relative motion of the camera~\cite{szeliski2010}.
\Cref{fig:orbslam_localization} shows a visualization of the localization process from the imagery. 
Through monocular images it is not possible to compute the position of the camera relative to the inertial frame.
Rather, it is only possible to determine a camera pose accurate to an unknown scale factor. 
This limitation is intrinsic to the transformation of the three-dimensional scene onto the two-dimensional image plane~\cite{szeliski2010}.
However, it is possible to compute the relative motion between sequential images and we use this to estimate the motion of the camera.
\begin{figure}[htbp]
    \captionsetup[subfigure]{position=b}
    \centering
    \subcaptionbox{Feature tracking visualization\label{fig:orbslam_mappoints}}{\includegraphics[width=0.5\textwidth]{figures/orbslam_mappoints.png}}~
    \subcaptionbox{Localization from monocular images\label{fig:orbslam_localization}}{\includegraphics[width=0.5\textwidth]{figures/orbslam_localization.png}}
    \caption{ORB-SLAM2 feature detection and localization from imagery~\label{fig:orbslam}}
\end{figure}

@@

\section{Conclusions}\label{sec:conclusions}
There have been a variety of approaches for the analysis and design of orbital trajectories around asteroids.
Relatively less work has been directed towards the design of landing trajectories.
Furthermore, much of the previous work has only treated the orbital or translational dynamics.
The approximation of a spacecraft as a point mass rather than an extended rigid body severely limits the applicability and ignores a major component of the dynamic environment.
This work directly derives the equations of motion of a dumbbell spacecraft around an asteroid described using a polyhedron potential model. 
We explicitly consider the impact of the gravitational moment on both the orbit and attitude dynamics. 
With this accurate equations of motion we develop geometric nonlinear controllers which allow for the vehicle to track a desired landing trajectory. 
The desired landing trajectory is accurately followed by the nonlinear controller on \SE.
Furthermore, we use current image processing techniques to estimate the motion of the spacecraft given only two-dimensional images. 
Inspite of the challenging environment, with limited lighting and a reduced simulation span, the method is able to accurately track the motion of the vehicle. 
Future work will focus on utilizing this estimate in a closed-loop control and guidance scheme to enable autonomous landing and obstacle avoidance. 
\bibliographystyle{AAS_publication} 
\bibliography{library}
% \bibliography{library_local}

>>>>

\begin{abstract}
    This paper considers the coupled orbit and attitude dynamics of a dumbbell spacecraft around an asteroid. 
    Geometric methods are used to derive the coupled equations of motion, which are defined on the configuration space of the special Euclidean group, and then a nonlinear controller is designed to enable trajectory tracking of desired landing trajectories.
    Rather than relying on sliding mode control or optimization based methods, the proposed approach avoids the increased control utilization and computational complexity inherent in other techniques.
    The nonlinear controller is used to track a desired landing trajectory to the asteroid surface. 
    A monocular imaging sensor is used to provide position and attitude estimates using visual odometry to enable relative state estimates.
    We demonstrate this control scheme with a landing simulation about asteroid Itokawa.
\end{abstract}

@@

Determination of the state of the spacecraft is typically dependent on ground based observations with sporadic state updates.
An additional capability is possible by using on-board sensors to estimate the state of the spacecraft relative to the asteroid~\cite{kubota2003,miso1999}.
We seek to incorporate localization using monocular images into the geometric nonlinear controller. 
This will offer the ability to increase the accuracy and frequency of state estimates and allow for closed loop control for landing operations. 
The use of imagery also enables the use of computer vision algorithms and tools to estimate the shape and motion of the asteroid.
The combination of visual localization and geometric control is a new avenue for the operation of spacecraft near asteroids.

@@

\subsection{Itokawa Shape Model and Simulated Imagery}\label{sec:imagery}
In this work, we consider trajectories about asteroid 25413 Itokawa.
Itokawa was the target of the Hayabusa mission and detailed shape and surface maps have been generated~\cite{kawaguchi2006,tanimoto2013,fujiwara2006}.
We use the estimated rotation period of \SI{12.1}{\hour} with a nominal density of \SI{1.9}{\gram\per\centi\meter\cubed} in the polyhedron potential model.
The shape model is composed of \num{786432} triangular faces and a rendering of the asteroid is provided in~\cref{fig:itokawa_3d}.
A highly detailed model is used for the shape of the asteroid to provide a more detailed and feature rich imaging target. 
However, the polyhedron potential model uses a much coarser shape composed of \num{64} faces. 
This greatly reduces the complexity of the potential model without a significant difference in the qualitative nature of the dynamic environment.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.5\textwidth, keepaspectratio]{figures/itokawa_blender.png}
    \caption{Blender Rendering of Asteroid 25413 Itokawa}
    \label{fig:itokawa_3d}
\end{figure}

Images of asteroid Itokawa are simulated using Blender, a free and open-source computer graphics software program~\cite{blenderfoundation1995--2017}.
Blender is primarily used by the animation and computer modeling fields to create computer generated images, videos and animations for films and video games. 
Blender offers the capability of accurately modeling the various effects of camera, lighting, and surface properties of a scene using the \texttt{cycles} path-tracing rendering engine.
A unique feature is the ability to compile the Blender rendering software as a Python module.
This allows one to use the capabilities of Blender through a Python API in personal scripts and functions programmatically, rather than through a desktop based graphical interface.
A camera is simulated within Blender with the parameters shown in~\cref{tab:camera_parameters}, which are chosen to emulate the primary sensor of the NEAR spacecraft~\cite{hawkins1997}.
\begin{table}
    \centering
\begin{tabular}{llr}  
\toprule
Parameter & Description &  Value\\
\midrule
FOV & horizontal field of view & \SI{2.25}{\degree}       \\
    &    vertical field of view  & \SI{2.90}{\degree}\\
Image Size & horizontal & \SI{537}{\px}\\
           & vertical & \SI{244}{\px}\\
\(f\)& focal length & \SI{167.35}{\milli\meter}\\
\bottomrule
\end{tabular}
\caption{Camera parameters used in simulation~\label{tab:camera_parameters}}
\end{table}

@@

In order to determine the attitude control input, we first define a desired attitude tracking command.
An arbitrary smooth attitude tracking command \( R_d (t) \in \SO \) is given as a function of time.
The corresponding angular velocity command is obtained using the attitude kinematics equation, \( \hat{\Omega}_d = R_d^T \dot{R}_d \).
With the desired attitude command, we then define the errors associated with the attitude and angular velocity.
The attitude and angular velocity tracking errors must be careful chosen to remain on the tangent bundle of \SO.
First, an attitude error function is defined on \( \SO \times \SO \) as
\begin{align}\label{eq:attitude_error_function}
    \Psi(R, R_d) = \frac{1}{2} \tr{I - R_d^T R}.
\end{align}
This positive definite function parameterizes the error between the current attitude, \( R \), and the desired attitude command \( R_d \).
Using the variations of \( \Psi \) gives the attitude tracking error vector \( e_R \in \R^3 \) as
\begin{align}\label{eq:attitude_error_vector}
    e_R = \frac{1}{2} \parenth{R_d^T R - R^T R_d^\vee}.
\end{align}
After further manipulation and using the attitude kinematics equation from~\cref{eq:attitude_kinematics}, it is possible to define the angular velocity tracking error \( e_\Omega \in \R^3 \) as
\begin{align}\label{eq:angular_velocity_error_vector}
    e_\Omega = \Omega - R^T R_d \Omega_d .
\end{align}
With the properly defined attitude error vectors the rotational control input is defined as 
\begin{align*}\label{eq:rotational_control}
    \vb{u}_m = - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - J \parenth{\hat{\Omega} R^T R_d \Omega_d - R^T R_d \dot{\Omega}_d} - \vb{M}_1 - \vb{M_2} 
\end{align*}
where \( k_R, k_\Omega \) are positive controller constants.

@@

We seek to utilize well-proven methods in the computer vision and robotics community to first localize the position of the spacecraft from visual imagery.
A secondary step, which is left to a subsequent publication, is then to use this imagery to autonomously update the position of the spacecraft while simultaneously mapping the surface. 
We utilize the state of the art ORB-SLAM implementation to estimate the state of the spacecraft using monocular images~\cite{mur-artal2015}.
This method provides a feature based monocular SLAM system that can operate in real-time for a wide variety of environments. 
ORB-SLAM builds on proven methods in the robotics community to create a custom SLAM system that provides for autonomous tracking and mapping in an unknown environment. 
The first step in ORB-SLAM is to determine accurate features within an image that are most easily recognized in subsequent images. 
This ``feature-extraction'' stage uses the FAST feature detector to determine suitable features, and then the ORB feature descriptor to a store a compact, scale-invariant description of the feature properties.
Next, these features are matched to subsequent images in a ``feature-matching'' stage to determine correspondance between subsequent images. 
For example,~\cref{fig:itokawa_feature_matching} shows a demonstration of features computed in two view of asteroid Itokawa. 
In addition, the correspondance is accurately computed between matching features as shown by the horizontal lines across both images.
From these correspondences, the pose of the camera system is estimated and predicted forward in time using a constant velocity model.
In a simultaneous thread, the ORB-SLAM system builds a local map and stores feature data in order to perform loop closure in the event of returning to a previously imaged location.
We utilize ORB-SLAM to provide an estimate of the position of the rigid spacecraft and will use this estimate to compute the control input.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth,keepaspectratio]{figures/itokawa_feature_matching.png}
    \caption{Demonstration of feature detection and matching between simulated images of asteroid 25413 Itokawa}
    \label{fig:itokawa_feature_matching}
\end{figure}
\section{Numerical Simulation}\label{sec:simulation}

We present a numerical simulation of a rigid dumbbell about asteroid Itokawa.
The dumbbell spacecraft is composed of two equal masses, \( m_1, m_2 = \SI{500}{\kilo\gram} \), separated by \( l = \SI{3}{\meter} \).
The dumbbell body frame is defined with the first body fixed axis, \( \vb{b}_1 \), originating at the center of mass of the spacecraft and directed along the vector from \( m_1 \) towards \( m_2 \).
The other two axes of the spacecraft fixed frame are chosen orthogonal to the \( \vb{b}_1 \) and lie in the plane orthogonal to the dumbbell axis of symmetry. 
A camera, using the parameters from~\cref{tab:camera_parameters}, is aligned with the \( \vb{b}_1 \) axis and used to feed image data to the ORB-SLAM system.
A numerical simulation is used to demonstrate the geometric control of the coupled motion of the spacecraft, and the ability to estimate the motion of the spacecraft from monocular imagery.

@@

The desired attitude command is chosen such that the spacecraft camera axis, \( \vb{b}_1 \), is directed along the nadir towards the asteroid.
It is sufficient to define two orthogonal vectors to uniquely determine the attitude of the spacecraft.
The \( \vb{b}_{3d} \) vector is chosen to lie in the plane spanned by \(\vb{b}_{1d} \) and \( \vb{e}_3 = \vb{f}_3 \).
The desired attitude command is defined as
\begin{align}
    \vb{b}_{1d} &= - \frac{\vb{x}}{\norm{\vb{x}}} , \\
    \vb{b}_{3d} &= \frac{\vb{f}_3 - \parenth{\vb{f}_3 \cdot \vb{b}_{1d}} \vb{b}_{1d}}{\norm{\vb{f}_3 - \parenth{\vb{f}_3 \cdot \vb{b}_{1d}} \vb{b}_{1d}}}, \\
    \vb{b}_{2d} &= \vb{b}_{3d} \times \vb{b}_{1d} , \\
R_d &= \begin{bmatrix} \vb{b}_{1d} & \vb{b}_{2d} & \vb{b}_{3d} \end{bmatrix} .
\end{align}
The camera axis is aligned with the spacecraft \( \vb{b}_ 1 \) axis, which is directed towards the asteroid, throughout the landing trajectory as the spacecraft moves in the equatorial plane of the asteroid.

The simulation is carried out over \SI{7200}{\second} with the spacecraft following a circular trajectory for the first \SI{3600}{\sec} before vertically descending in the body fixed frame for the last \SI{3600}{\second}.
\Cref{fig:true_landing_trajectory} shows a view from the positive \( \vb{f}_3 \) pole of the asteroid of the simulated trajectory. 
The position of the center of mass of the dumbbell is shown in blue, while the pointing direction of the camera axis is defined in red. 
The attitude of the dumbbell is displayed at several points along the trajectory demonstrating the pointing of the camera. 
Furthermore, asteroid Itokawa is shown in its final orientation at the completion of the landing simulation. 
\Cref{fig:pos_components} shows that the nonlinear controller is able to accurately track the desired translational trajectory for the duration of the simulation.
\begin{figure}[htbp]
    \captionsetup[subfigure]{position=b}
    \centering
    \subcaptionbox{Planar view of landing trajectory\label{fig:true_landing_trajectory}}{\includegraphics[width=0.5\textwidth]{figures/traj_fig.pdf}}~
    \subcaptionbox{Position of spacecraft in the inertial frame\label{fig:pos_components}}{\includegraphics[width=0.5\textwidth]{figures/pos_fig.pdf}}
    \caption{Landing trajectory to asteroid Itokawa~\label{fig:position}}
\end{figure}

Concurrent with the simulation, we generate images of Itokawa using Blender, as described earlier.
The images are generated at a rate of \SI{1}{\hertz} and stored for post processing and one example view is shown in~\cref{fig:example_image}. 
From these images we estimate the position of the camera relative to the asteroid using monocular localization.
In this work, we demonstrate the ability to generate realistic imagery and the processing of these images to determine a state estimate of the camera pose.
In future work, we seek to use this state estimate in a closed-loop controller to enable a fully-autonomous control system for the spacecraft. 
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/test000837.png}
    \caption{Example image of Itokawa at \( t = \SI{837}{\second}\)\label{fig:example_image}}
\end{figure}
From each image, a series of features are detected and tracked between subsequent frames.
A visualization of this process is shown in~\cref{fig:orbslam_mappoints} which shows the tracked features of the image in green.
From these tracked features it is possible to estimate the relative motion of the camera~\cite{szeliski2010}.
\Cref{fig:orbslam_localization} shows a visualization of the localization process from the imagery. 
Through monocular images it is not possible to compute the position of the camera relative to the inertial frame.
Rather, it is only possible to determine a camera pose accurate to an unknown scale factor. 
This limitation is intrinsic to the transformation of the three-dimensional scene onto the two-dimensional image plane~\cite{szeliski2010}.
However, it is possible to compute the relative motion between sequential images and we use this to estimate the motion of the camera.
\begin{figure}[htbp]
    \captionsetup[subfigure]{position=b}
    \centering
    \subcaptionbox{Feature tracking visualization\label{fig:orbslam_mappoints}}{\includegraphics[width=0.5\textwidth]{figures/orbslam_mappoints.png}}~
    \subcaptionbox{Localization from monocular images\label{fig:orbslam_localization}}{\includegraphics[width=0.5\textwidth]{figures/orbslam_localization.png}}
    \caption{ORB-SLAM2 feature detection and localization from imagery~\label{fig:orbslam}}
\end{figure}

@@

\section{Conclusions}\label{sec:conclusions}
There have been a variety of approaches for the analysis and design of orbital trajectories around asteroids.
Relatively less work has been directed towards the design of landing trajectories.
Furthermore, much of the previous work has only treated the orbital or translational dynamics.
The approximation of a spacecraft as a point mass rather than an extended rigid body severely limits the applicability and ignores a major component of the dynamic environment.
This work directly derives the equations of motion of a dumbbell spacecraft around an asteroid described using a polyhedron potential model. 
We explicitly consider the impact of the gravitational moment on both the orbit and attitude dynamics. 
With this accurate equations of motion we develop geometric nonlinear controllers which allow for the vehicle to track a desired landing trajectory. 
The desired landing trajectory is accurately followed by the nonlinear controller on \SE.
Furthermore, we use current image processing techniques to estimate the motion of the spacecraft given only two-dimensional images. 
In spite of the challenging environment, with limited lighting and a reduced simulation span, the method is able to accurately track the motion of the vehicle. 
Future work will focus on utilizing this estimate in a closed-loop control and guidance scheme to enable autonomous landing and obstacle avoidance. 
\bibliographystyle{AAS_publication} 
\bibliography{library}
% \bibliography{library_local}
